Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-03 doc/paper.Rmd
not sure what I changed

\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\gk}[1]{{\textcolor{green}{#1}}}
\newcommand{\cited}[1]{{\textcolor{red}{#1}}}
\setlength\parindent{0pt}

@@

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
#  ref: http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
```

@@

\hh{In the next page and a half it is easy to lose the red line. It might help to include a table with an overview.
The table should include the reference to the paper, the data used, the statistical method and the associated error rates.}
Various toolmarks have been studied in the literature:  \citet{manytoolmarks1} and \citet{chumbley} have been analyzing screwdriver marks  digitized using a profilometer;  \citet{manytoolmarks2} have investigated 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope; \citet{afte-chumbley} have been investigated digitized marks from slip-joint pliers generated by a surface profilometer.

\hh{We need an additional sentence here to get from the data to the statistical methods ... }
\citet{manytoolmarks2} define a relative distance metric and use it as similarity measure between two toolmarks. \citet{manytoolmarks1} extract many small segments in the markings of two toolmarks and compare similiarity using a maximum pearson correlation coefficient. 
The Chumbley scoring method, first introduced by \citet{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  \citep{hadler} make the score deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segements of striae.  In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assess striation marks on bullet lands for same-source identification.

@@

@@

@@

roc.summary <- cvcs %>% group_by(wo, wv, method) %>%
  summarize(
    eer = EER(1-p_value, match),
    auc = AUC(1-p_value, match)
  )
p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Equal Error rate (EER)") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = c(0.3, 0.2))

p2 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=auc, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Area under the curve (AUC)") +
  xlab("Size of optimization window in pixels")+
  theme(legend.position = c(0.7, 0.2))
grid.arrange(p1, p2, nrow=1)
```

@@

```{r prof_missings, fig.width=10, fig.height=10, fig.cap="Row 3:  Total error and Number of failed tests by the window validation size, wv, and ground truth, Row 2: Total error and Number of failed tests with Coarseness for both profiles and signatures, Row 1: Type II error for different coarseness levels as used in the modified chumbley algorithm for profiles and signatures"}

>>>>

\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\gk}[1]{{\textcolor{blue}{#1}}}
\newcommand{\cited}[1]{{\textcolor{red}{#1}}}
\setlength\parindent{0pt}

@@

@@

\hh{In the next page and a half it is easy to lose the red line. It might help to include a table with an overview.
The table should include the reference to the paper, the data used, the statistical method and the associated error rates.}
\gk{table included}
Various toolmarks have been studied in the literature:  \citet{manytoolmarks1} and \citet{chumbley} have been analyzing screwdriver marks  digitized using a profilometer;  \citet{manytoolmarks2} have investigated 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope; \citet{afte-chumbley} have been investigated digitized marks from slip-joint pliers generated by a surface profilometer.

\hh{We need an additional sentence here to get from the data to the statistical methods ... }
\gk{Analysis of these digitized markings require the use of statistical methods which can quantify the scientific mechanism of comparing markings and serve as metrics for correctly identifying the error rate.}
\citet{manytoolmarks2} define a relative distance metric and use it as similarity measure between two toolmarks. \citet{manytoolmarks1} extract many small segments in the markings of two toolmarks and compare similiarity using a maximum pearson correlation coefficient. 
The Chumbley scoring method, first introduced by \citet{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  \citep{hadler} make the score deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segements of striae.  In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assess striation marks on bullet lands for same-source identification.

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Research paper & Method & Data Source & False Positives & False Negatives\\
  \hline
 \textbf{\citet{manytoolmarks1}} & Maximized & Screwdrivers & & \\ & Correlation &  & - & - \\ \hline
 \textbf{\citet{chumbley}} & Randomized & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 2.3\% & 8.9\%  \\ \hline
  \textbf{\citet{afte-chumbley}} & Randomized & Slip-joint  &  & \\ & Chumbley Score &  & - & - \\ \hline 
  \textbf{\citet{hadler}} & Deterministic & Screwdrivers & & \\ (Same-Surface Same-Angle) & Chumbley Score & & 0\% & 6\%  \\ \hline
  \textbf{\citet{manytoolmarks2}} & Similarity Measure & Screwdrivers & & \\ (Different Surfaces-same angle) & Relative Distance Metric & & 5.9\% &  9.4\% \\ (Same Surfaces-same angle)&  & & 0.22\% &  0\% \\
   \hline
\end{tabular}}
\caption{\label{tab:toolmarks-ER} Error Rates for Toolmarks using  variations of the chumbley score method}
\end{table}

 <!-- \textbf{\citet{manytoolmarks2}} & Similarity Measure & Screwdrivers & & \\ (Different Surfaces-same angle) & Relative Distance Metric & & 5.9\% &  9.4\% \\ (Same Surfaces-same angle)&  & & 0.22\% &  0\% \\ -->

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=0.62\textwidth]{images/same-shift-failure.png}

\caption{\label{same-shift-failure}Sketch of same-shift pairings  (top) when the lag is too large to accomodate a a vaildation window in either of the two signatures}
\end{figure}

\begin{figure}[hbtp]
\centering
\includegraphics[width=0.7\textwidth]{images/diff-shift-failure.png}

\caption{\label{diff-shift-failure}Sketch of diff-shift pairings  (top) when the number of diff-shift computations is likely to 0}
\end{figure}

\begin{figure}[hbtp]
\centering
\includegraphics[width=.7\textwidth]{images/CS1-failure-CS2-success.png}
\caption{\label{CS1-failure-CS2-success}Sketch of a case where CS1 fails but CS2 does not fail}
\end{figure}

@@

\gk{The key effect of the optimal locations and thereby the coarseness is seen in the number of failed tests. Irrespective of whether CS1 or CS2 is being used, if the relative optimal locations are at the boundaries we will see an increase in the number of failed tests. A balance is therefore needed in the selection of the coarseness parameter which reduces the boundary effect but also does not remove important (sub-)class characteristics}

@@

roc.summary <- cvcs %>% group_by(wo, wv, method) %>%
  summarize(
    eer = EER(1-p_value, match),
    auc = AUC(1-p_value, match)
  )
p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Equal Error rate (EER)") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = c(0.25, 0.25))

p2 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=auc, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Area under the curve (AUC)") +
  xlab("Size of optimization window in pixels")+
  theme(legend.position = c(0.75, 0.25))
grid.arrange(p1, p2, nrow=1)
```

@@

```{r prof_missings, fig.width=10, fig.height=10, fig.cap="Row 3:  Total error and Number of failed tests by the window validation size, wv, and ground truth, Row 2: Total error and Number of failed tests with Coarseness for both profiles and signatures, Row 1: Type II error for different coarseness levels as used in the modified chumbley algorithm for profiles and signatures", eval = FALSE}
